Lessons learned from bugs in models of human history

### 2020-05-20 paper.tex

\title{Lessons learned from buggy models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
Lessons learned from misspecified models of human history \\
Lessons learned from buggy models of human history \\
Lessons learned from bugs in population genetics models
}

@@

\section*{A bad tutorial example}

@@

\section*{Risk prediction in human populations}

@@

\section*{Acknowledgements}

\begin{itemize}
\item Alicia Martin
\item stdpopsim as a whole or anyone in particular from that group?
\item others?
\end{itemize}

>>>>

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
Lessons learned from misspecified models of human history \\
Lessons learned from buggy models of human history \\
Lessons learned from bugs in population genetics models
}
\sgcomment{How to avoid simulating the wrong demographic model}

@@

\section*{Case 1: A misspecified model in msprime's documentation}

@@

\section*{Case 2: Incorrect model parameters in an analysis pipeline}

@@
